Synthesizing Symmetric Lenses

### 2019-01-29 papers/SymmetricLenses/main.tex
Checkpoint

This infrastructure gives us what we need to find likely satisfying lenses from
a collection of satisfying lenses. All such lenses must synchronize data between
the same two SREs $\Regex$ and $\RegexAlt$. For any such lens $\Lens$, we can
calculate the expected number of bits required to recover a string $t$ in
$\LanguageOf{\RegexAlt}$ from a synchronized string $s$ in
$\LanguageOf{\Regex}$. This expectation is the \emph{conditional entropy of
  $\Regex$ given $\RegexAlt$ and $\Lens$}, formally $\sum_{s \in
  \Regex}\ProbabilityOf{\Regex}{s}\EntropyOf{\SetOf{t \SuchThat
    \Lens.\PutROf{s}{t} = t}}$. The likelihood we assign to $\Lens$ is the sum
of the conditional entropy of $\Regex$ given $\RegexAlt$ and $\Lens$ and the
conditional entropy of $\RegexAlt$ given $\Regex$ and $\Lens$. This metric
assigns higher entropy (or cost) to lenses where knowing the string
on one side 
provides little information about the string on the other side. 
It assigns zero entropy to bijections because given a string $s \in \Regex$,
the bijection exactly determines
the corresponding string in 
$\RegexAlt$.

>>>>

\bcp{This paragraph has a funny flow: The first sentence implies that
  entropy is all we need.  The second sentence then says that, actually, we
  need something else!}Entropy is the tool we need to
choose likely satisfying lenses from 
a collection of satisfying lenses. All such lenses must synchronize data between
the same two SREs $\Regex$ and $\RegexAlt$. For any lens $\Lens$, we can
calculate the expected number of bits required to recover a string $t$ in
$\LanguageOf{\RegexAlt}$ from a synchronized string\bcp{Have we defined
  what a ``synchronized string'' is?} $s$ in
$\LanguageOf{\Regex}$.  This expectation is the \emph{conditional entropy of
  $\Regex$ given $\RegexAlt$ and $\Lens$}, formally $\sum_{s \in
  \Regex}\ProbabilityOf{\Regex}{s}\cdot\EntropyOf{\SetOf{t \SuchThat
    \Lens.\PutROf{s}{t} = t}}$.\bcp{It seems H is applied here to one argument.  Are
  we supposed to know what that means.} The likelihood we assign to $\Lens$ is the sum
of the conditional entropy of $\Regex$ given $\RegexAlt$ and $\Lens$ and the
conditional entropy of $\RegexAlt$ given $\Regex$ and $\Lens$. This metric
assigns higher entropy (or cost) to lenses where knowing the string
on one side 
provides little information about the string on the other side. 
It assigns zero entropy to bijections because given a string $s \in \Regex$,
the bijection exactly determines
the corresponding string in 
$\RegexAlt$.
